### 2017-03-14 thesis/latex/thesis.tex
Thesis: minor commit.

\tableofcontents
\newpage

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
  \caption{Artist rendition of the dynein motor bound to a microtubule. One monomer is bound to the MT, and one is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
  \label{dynein-artist-rendition}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
  \caption{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
  \label{diffusion_vs_dynein}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/retrograde_transport.jpg}
  \caption{Mechanism of dynein localization to axon tips, or growth cones, in retrograde transport mediated by kinesin anterograde transport. Modified from \cite{valetoolbox}.}
  \label{retrograde-transport}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
  \caption{Artist rendition of the dynein motor bound to a microtubule. One monomer is bound to the MT, and one is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
  \label{dynein-artist-rendition-2}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures//burgess-dynein-angles}
  \caption{Cryo-electron microscopy images of dynein in two different nucleotide states. Left: dynein frozen in ADP-Pi state. Middle: dynein without nucleotide. Right: two states superimposed on one another. Bottom: cartoons representing how dynein may bind to the MT in either state. From \cite{burgess-paper}.}
  \label{fig:cryo-em-angles}
\end{figure}

Crystal structures of cytoplasmic dynein-2, a relative of dynein, indicate that ATP-Pi binding to the motor domain induces a conformation change in the motor domain, which alters the angle at which the motor binds to the tail \cite{carter-paper}. Taken together, these results indicate that as the motor binds and hydrolyzes ATP, it undergoes a conformation change which physically moves the motor relative to the tail. This movement might cause a net forward motion of the motor domain.\\

@@

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/weihong-step-size}
    \caption{Size of steps taken by dynein motor parallel to microtubule. Positive axis corresponds to steps towards the microtubule minus-end. Figure modified from \cite{weihongpaper}.}
  \end{minipage}
  \hspace{.2cm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/weihong-off-axis-steps}
    \caption{Size of ``off-axis'' steps taken by the dynein motor perpendicular to the microtubule. Figure modified from \cite{weihongpaper}.}
  \end{minipage}
  \label{fig:weihong-steps}
\end{figure}

\subsection{Dynein models}
Data presented in the previous sections paints a

\subsubsection{Cianfrocco Model}
Cianfrocco \textit{et. al} \cite{cianfroccoreview} propose dynein achieves motion via transitioning through the cycle of states shown in Fig. \ref{mech-cycle}. This model will hereon be referred to as the Cianfrocco model. The model claims the primary events in the dynein step are as follows. First, starting with both binding domains attached to the MT, ATP binds to the motor domain, which causes it to change conformation. ATP hydrolysis to ADP-Pi causes further conformation changes. These changes cause the binding domain to release the microtubule, meaning only one binding domain is MT-bound. The free binding domain then undergoes another conformation change known as the ``priming stroke,'' which changes the orientation of the binding domain with respect to the MT. Finally the binding domain rebinds to the MT, causing a final conformation change in the motor which returns it to the beginning of the cycle. The exact order of these events is not precisely known. More detail on each step of the cycle is given below.\\

Maybe show the Cianfrocco model in a section \textit{after} talking about all the things which happen for sure in dynein, since it's more theoretical? Talk about the Cianfrocco model, but other interpretations?

Make a figure of pre/post-powerstroke dynein with the linker hilighted? Can you get what residues correspond to the linker somewhere?

\begin{figure}[h!]
  \centering
  \includegraphics[width=.90\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
  \newcommand\bothbound{\textcolor{blue}{BOTHBOUND}}
  \newcommand\onebound{\textcolor{red}{ONEBOUND}}
  \newcommand\transition{\textcolor{green}{transition?}}
  %% \begin{tabular}{rll}
  %%   \bothbound &
  %%   1 & \begin{minipage}{5in}
  %%     Bound to microtubule and waiting for ATP to arrive.  The
  %%     conformation is ``post-powerstroke''.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   2 & \begin{minipage}{5in}
  %%     ATP has bound to the motor at AAA1, but nothing else has changed.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \transition &
  %%   3 & \begin{minipage}{5in}
  %%     ``The ring has closed'' in the motor, whatever that means.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   4 & \begin{minipage}{5in}
  %%     The affinity to the microtubule is dropped, so it is likely to pop off soon.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \onebound &
  %%   5 & \begin{minipage}{5in} It has popped off of the microtubule!
  %%     Onebound! The equilibrium angle is also changed.  The ATP has
  %%     been hydrolized, but the phosphate is still bound to the motor.
  %%     ``Priming stroke?''
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \onebound &
  %%   6 & \begin{minipage}{5in} It is now bound to the microtubule, but
  %%     with low affinity, and without any loss of phosphate. Question:
  %%     does this happen many times? If so it may still be onebound.
  %%     Otherwise it is probably bothbound.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   7 & \begin{minipage}{5in}
  %%     Now it is seriously bound to the microtubule, and the motor
  %%     domain has changed conformation.  This is now ``high affinity.''
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   8 & \begin{minipage}{5in}
  %%     Phosphate has been released, and our equilibrium angles have
  %%     been changed.  This is the ``power stroke.''
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   1 & \begin{minipage}{5in}
  %%     The ADP has been released from the motor domain, so it can now
  %%     bind ATP.  Still ``high affinity,'' and still in the
  %%     ``power-stroke'' conformation.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   9 & \begin{minipage}{5in}
  %%     While stuck in this ``normal bound'' state, another site on the
  %%     motor AAA3 can lose its ADP, which leaves the motor in a state
  %%     where it cannot directly move on to step 2 (until after
  %%     reversing this).  Controversial?
  %%   \end{minipage}
  %% \end{tabular}
  \caption{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
  \label{mech-cycle}
\end{figure}

\subsubsection{Other models}
If there are other models which conflict with Cianfrocco, here would be a place to put them.\\

\subsection{This work}
\subsubsection{Our model}
what we're trying to do with our project

@@

\section{Chapter: Theory}
\subsection{Model features}
The purpose of this project is to find if a minimal set of features is capable of reproducing dynein's stepping behavior. To test this hypothesis, these features are put into a model and simulated. The features are as follows:

\begin{itemize}
\item Dynein is a collection of spherical domains joined together by massless rods
\item These rods are rigid
\item Each joint in the motor feels a spring force about some equilibrium joint angle
\item Dynein can be in two states: onebound and bothbound
\item Onebound has one domain bound to the floor and takes on onebound equilibrium angles
\item Bothbound has two domains bound to the floor and takes on bothbound equilibrium angles
\item Transitions between the two states are based solely on spring energies between the two models
\item Brownian dynamics describes the behavior of the domains in time
\item Binding at $\alpha-\beta$ tubulin binding sites is not necessary for stepping
\item Stepping can be described by a 2D model; forces in the MT-perpendicular direction are not necessary for stepping
\end{itemize}

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/ob_fig}
  \caption{}
  \label{fig:model-intro}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../../figures/code-onebound}
  \includegraphics[width=.45\textwidth]{../../figures/code-bothbound}
  \caption{Representations of onebound (left) and bothbound (right) dynein models.}
  \label{ob_fig}
\end{figure}

@@

\subsubsection{$\alpha-\beta$ binding unnecessary}
Dynein binds to a site on the $\alpha-\beta$ tubulin polymer microtubule which repeats roughly every 8nm. Thus, all dynein steps should be multiples of $8$nm. This model ignores this requirement and allows stepping to occur at any length. This assumption is not based on biology, but to simplify the model. The assumption is that \textit{in vivo} dynein is tuned to take 8nm steps based on its size and stepping angle, and doesn't search along the MT for a binding site.\\

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../../figures/weihong-side-stepping}
  \caption{Angular histogram of off-axis stepping of dynein, as found by \cite{weihongpaper}. 0 degrees corresponds to a step parallel to the MT, and 270 degrees a step purely to the right. Modified.}
  \label{fig:weihong-side-stepping}
\end{figure}

@@

The four angles $\Theta_{bb}, \Theta_{bm}, \Theta_{um}$ and $\Theta_{ub}$, corresponding to bound binding, bound motor, unbound motor and unbound binding angle, together describe any possible conformation the system can take on. The domain of $\Theta_{bb}$ has a restricted domain of $[0,\pi]$ to prevent below-MT conformations, but the other angles have domains of $[0,2\pi]$. Each angle is defined relative to the horizontal axis.\\

\begin{figure}[h]
  \centering
  \begin{tabular}{c}
    \begin{lstlisting}[language=C++]
      class Dynein_onebound{
        double &$\Theta_{bb}, \Theta_{bb}, \Theta_{bb}, \Theta_{bb}$&
        double &$\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$&
        double &$X_{bb}$&
      }
    \end{lstlisting}
  \end{tabular}
  \caption{Pseudocode of the onebound Dynein model.}
  \label{ob_struct}
\end{figure}

Pseudocode for the numerical onebound model representation is shown in Figure \ref{ob_struct}. The position of the bound binding domain $X_{bb}$ and the four domain angles are all the values needed to determine the position of the protein at any time.\\

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../../figures/code-bothbound.pdf}
  \caption{Definition of equilibrium angles.}
  \label{bb_fig}
\end{figure}

@@

      t += dt
    \end{lstlisting}
  \end{tabular}
  \caption{Code snippet of Euler's method to update the positions of the onebound model simultaneously.}
  \label{ob_struct}
\end{figure}

@@

\begin{figure}[h!]
  \begin{tabular}{c}
    \begin{lstlisting}[language=python]
      def get_near_unbinding_rate(dyn_bb) {
        dyn_ob_test = make_onebound_from_bothbound(dyn_bb) // do a fake unbind to find energy
        dG_spring = dyn_ob_test.get_PE() - dyn_bb.get_PE()
        low_affinity_unbinding_preexponential_factor = low_affinity_unbinding_rate / exp(1.0)
        return low_affinity_unbinding_preexponential_factor*exp(-dG_spring/kb/T)
      }
      def transition_bothbound_to_onebound(dyn_bb) {
        random_number = rand(0,1)
        if (random_number < get_unbinding_rate(dyn_bb)) {
          return make_onebound_from_bothbound(dyn_bb)
        }
        else return 0
      }
    \end{lstlisting}
  \end{tabular}
  \caption{Code snippet of transition rate calculation using the Arrhenius equation.}
  \label{transition-rate-snippet}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{c}
    \begin{lstlisting}[language=C++]
      T = cm*(nma - nma_eq);
      f1 = T/Ls;
      f2 = T/Lt;
      f1x = f1 * sin(bba);
      f1y = f1 * -cos(bba);
      f2x = f2 * sin(bma);
      f2y = f2 * -cos(bma);
      f.bbx += f1x;
      f.bby += f1y;
      f.tx  += f2x;
      f.ty  += f2y;
      f.bmx += -(f1x + f2x); // equal and opposite forces
      f.bmy += -(f1y + f2y);
    \end{lstlisting}
  \end{tabular}
  \caption{Code snippet of internal force calculation.}
  \label{transition-rate-snippet}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
    \caption{Average domain PE of onebound model converging to $\frac12 k_BT$ energy over time.}
  \end{minipage}
  \hspace{.2cm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
    \caption{Total domain PE of bothbound model converging to $\frac12 k_BT$ energy over time.}
  \end{minipage}
  \label{fig:equipartition_agreement}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| c | c | c | c |}
    \hline
    Author & Conditions & Velocity & Run length\\\hline
    Qiu \cite{weihongpaper} & 1mM [ATP] & $134 \pm 60.4$ nm & $1.06 \pm 0.044 \mu m$\\ \hline
    Reck-Peterson \cite{reck2006single} & 1mM [ATP] & $85 \pm 30 nm/s$  & $1.9 \pm 0.2 \mu m$\\ \hline
  \end{tabular}
  \caption{Table of literature values for dynein behavior}
  \label{table:parameter-table}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l | l | l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
    $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
    $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
    $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
    $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
    $R_t$ &  & & & & 2.16nm & & & \\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
    $k_b$ & $460 s^{-1,b}$ & & & & & & & \\ \hline
    $c_t$ & & & & & & & & \\ \hline
    $c_m$ & & & & & & & & \\ \hline
    $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
  \end{tabular}
  \caption{Table of literature values for various free parameters in dynein model.}
  \label{table:parameter-table}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l |}
    \hline
    T & [ATP] \\ \hline
    310.15 K & $1mM$\\ \hline
  \end{tabular}
  \caption{Table of physical constants used in simulation.}
  \label{table:parameter-table}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../../figures/SarlahParameterTable.png}
  \caption{Kinetic rates used in Sarlah \textit{et. al.}'s model \cite{sarlahmodel}.}
  \label{fig:sarlah-rate-table}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| c | c | c | c | c | c |}
    \hline
    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
    134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
  \end{tabular}
  \caption{Table calculating estimates for $\tbb$ and $\tob$.}
  \label{table:parameter-table}
\end{figure}

>>>>

\tableofcontents
\listoffigures
\newpage

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
  \caption{Artist's rendition of dynein.}{Artist rendition of the dynein motor bound to a microtubule. One monomer is bound to the MT, and one is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
  \label{dynein-artist-rendition}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
  \caption{Passive diffusion vs motor transport rate}{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
  \label{diffusion_vs_dynein}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/retrograde_transport.jpg}
  \caption{Dynein localization to axon growth cones.}{Mechanism of dynein localization to axon tips, or growth cones, in retrograde transport mediated by kinesin anterograde transport. Modified from \cite{valetoolbox}.}
  \label{retrograde-transport}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
  \caption{Artist's rendition of motor-MT complex.}{Artist rendition of the dynein motor bound to a microtubule. One monomer is bound to the MT, and one is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
  \label{dynein-artist-rendition-2}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures//burgess-dynein-angles}
  \caption{Cryo-EM microscopy of dynein conformational states.}{Cryo-electron microscopy images of dynein in two different nucleotide states. Left: dynein frozen in ADP-Pi state. Middle: dynein without nucleotide. Right: two states superimposed on one another. Bottom: cartoons representing how dynein may bind to the MT in either state. From \cite{burgess-paper}.}
  \label{fig:cryo-em-angles}
\end{figure}

Crystal structures of cytoplasmic dynein-2, a relative of dynein, indicate that ATP-Pi binding to the motor domain induces a conformation change in the motor domain, which alters the angle at which the motor binds to the tail \cite{carter-paper} (make a Chimaera figure where the pre/poststroke motors are docked showing this). Taken together, these results indicate that as the motor binds and hydrolyzes ATP, it undergoes a conformation change which physically moves the motor relative to the tail.\\

@@

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/weihong-step-size}
    \caption{Experimental dynein step size histogram.}{Size of steps taken by dynein motor parallel to microtubule. Positive axis corresponds to steps towards the microtubule minus-end. Figure modified from \cite{weihongpaper}.}
  \end{minipage}
  \hspace{.2cm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/weihong-off-axis-steps}
    \caption{Dynein experimental off-axis stepping size.}{Size of ``off-axis'' steps taken by the dynein motor perpendicular to the microtubule. Figure modified from \cite{weihongpaper}.}
  \end{minipage}
  \label{fig:weihong-steps}
\end{figure}

\subsection{Dynein models}
Data presented in the previous sections paints a picture of dynein as a collection of interconnected parts, each cycling through its own collection of states and influencing other parts. Somehow the protein itneracts with nucleotides and microtubules in a way that allows it to reliably move through the cell. Models presented below take these facts and string them together into cohesive cycles which might explain how dynein walks. It is important to note that these models are hypotheses.\\

\subsubsection{Cianfrocco Model}
Cianfrocco \textit{et. al} \cite{cianfroccoreview} propose dynein achieves motion via transitioning through the cycle of states shown in Fig. \ref{mech-cycle}. This model will hereon be referred to as the Cianfrocco model. The model claims the primary events in the dynein step are as follows. First, starting with both binding domains attached to the MT, ATP binds to the motor domain, which causes it to change conformation. ATP hydrolysis to ADP-Pi causes further conformation changes. These changes cause the binding domain to release the microtubule, meaning only one binding domain is MT-bound. The free binding domain then undergoes another conformation change known as the ``priming stroke,'' which changes the orientation of the binding domain with respect to the MT. Finally the binding domain rebinds to the MT, causing a final conformation change in the motor which returns it to the beginning of the cycle. The exact order of these events is not precisely known.\\

\begin{figure}[h!]
  \centering
  \includegraphics[width=.90\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
  \newcommand\bothbound{\textcolor{blue}{BOTHBOUND}}
  \newcommand\onebound{\textcolor{red}{ONEBOUND}}
  \newcommand\transition{\textcolor{green}{transition?}}
  %% \begin{tabular}{rll}
  %%   \bothbound &
  %%   1 & \begin{minipage}{5in}
  %%     Bound to microtubule and waiting for ATP to arrive.  The
  %%     conformation is ``post-powerstroke''.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   2 & \begin{minipage}{5in}
  %%     ATP has bound to the motor at AAA1, but nothing else has changed.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \transition &
  %%   3 & \begin{minipage}{5in}
  %%     ``The ring has closed'' in the motor, whatever that means.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   4 & \begin{minipage}{5in}
  %%     The affinity to the microtubule is dropped, so it is likely to pop off soon.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \onebound &
  %%   5 & \begin{minipage}{5in} It has popped off of the microtubule!
  %%     Onebound! The equilibrium angle is also changed.  The ATP has
  %%     been hydrolized, but the phosphate is still bound to the motor.
  %%     ``Priming stroke?''
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \onebound &
  %%   6 & \begin{minipage}{5in} It is now bound to the microtubule, but
  %%     with low affinity, and without any loss of phosphate. Question:
  %%     does this happen many times? If so it may still be onebound.
  %%     Otherwise it is probably bothbound.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   7 & \begin{minipage}{5in}
  %%     Now it is seriously bound to the microtubule, and the motor
  %%     domain has changed conformation.  This is now ``high affinity.''
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   8 & \begin{minipage}{5in}
  %%     Phosphate has been released, and our equilibrium angles have
  %%     been changed.  This is the ``power stroke.''
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   1 & \begin{minipage}{5in}
  %%     The ADP has been released from the motor domain, so it can now
  %%     bind ATP.  Still ``high affinity,'' and still in the
  %%     ``power-stroke'' conformation.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   9 & \begin{minipage}{5in}
  %%     While stuck in this ``normal bound'' state, another site on the
  %%     motor AAA3 can lose its ADP, which leaves the motor in a state
  %%     where it cannot directly move on to step 2 (until after
  %%     reversing this).  Controversial?
  %%   \end{minipage}
  %% \end{tabular}
  \caption{Cianfrocco mechanochemical cycle.}{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
  \label{mech-cycle}
\end{figure}

%% \subsubsection{Other models}
%% Find other models and put them here

\subsection{Necessary and sufficient criteria for motion}
Each of the models described above postulates a series of chemical events which occur during the dynein step. Testing such hypotheses can be done in a variety of ways.

\subsubsection{Our model}
what we're trying to do with our project

@@

\section{Chapter: Theory}
\subsection{Model features}
The purpose of this project is to find if a minimal set of features is capable of reproducing dynein's stepping behavior. To test this hypothesis, these features are put into a model and simulated. A schematic of the model is pictured in Figure \ref{fig:model-intro} and described below.\\

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../../figures/code-onebound}
  \includegraphics[width=.45\textwidth]{../../figures/code-bothbound}
  \caption{Dynein model schematics.}{Representations of onebound (left) and bothbound (right) dynein models.}
  \label{ob_fig}
\end{figure}

%% \begin{itemize}
%% \item Dynein is a collection of spherical domains joined together by massless rods
%% \item These rods are rigid
%% \item Each joint in the motor feels a spring force about some equilibrium joint angle
%% \item Dynein can be in two states: onebound and bothbound
%% \item Onebound has one domain bound to the floor and takes on onebound equilibrium angles
%% \item Bothbound has two domains bound to the floor and takes on bothbound equilibrium angles
%% \item Transitions between the two states are based solely on spring energies between the two models
%% \item Brownian dynamics describes the behavior of the domains in time
%% \item Binding at $\alpha-\beta$ tubulin binding sites is not necessary for stepping
%% \item Stepping can be described by a 2D model; forces in the MT-perpendicular direction are not necessary for stepping
%% \end{itemize}

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/ob_fig}
%%   \caption{Onebound dynein model.}{}
%%   \label{fig:model-intro}
%% \end{figure}

@@

@@

\subsubsection{Binding to microtubule}
The model ``steps'' whenever an MTBD diffuses near the microtubule. \textit{In vivo}, dynein binds to a site on the $\alpha-\beta$ tubulin polymer microtubule which repeats roughly every 8nm. Thus, all dynein steps should be multiples of $8$nm. This model ignores this requirement and allows stepping to occur at any length. The assumption is that \textit{in vivo} dynein takes 8nm steps because of its size and stepping angle. Thus the 8nm step length should be reproduced by the model without explicit coding.\\

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../../figures/weihong-side-stepping}
  \caption{Dynein experimental off-axis stepping histogram.}{Angular histogram of off-axis stepping of dynein, as found by \cite{weihongpaper}. 0 degrees corresponds to a step parallel to the MT, and 270 degrees a step purely to the right. Modified.}
  \label{fig:weihong-side-stepping}
\end{figure}

@@

The four angles $\Theta_{bb}, \Theta_{bm}, \Theta_{um}$ and $\Theta_{ub}$, corresponding to bound binding, bound motor, unbound motor and unbound binding angle, together describe any possible conformation the system can take on. The domain of $\Theta_{bb}$ has a restricted domain of $[0,\pi]$ to prevent below-MT conformations, but the other angles have domains of $[0,2\pi]$. Each angle is defined relative to the horizontal axis. The position of the bound binding domain $X_{bb}$ and the four domain angles are all that is needed to determine the position of the protein at any time.\\

%% \begin{figure}[h]
%%   \centering
%%   \begin{tabular}{c}
%%     \begin{lstlisting}[language=C++]
%%       class Dynein_onebound{
%%         double &$\Theta_{bb}, \Theta_{bb}, \Theta_{bb}, \Theta_{bb}$&
%%         double &$\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$&
%%         double &$X_{bb}$&
%%       }
%%     \end{lstlisting}
%%   \end{tabular}
%%   \caption{Pseudocode of the onebound Dynein model.}
%%   \label{ob_struct}
%% \end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../../figures/code-bothbound.pdf}
  \caption{Model bothbound equilibrium angle defintion.}{}
  \label{bb_fig}
\end{figure}

@@

      t += dt
    \end{lstlisting}
  \end{tabular}
  \caption{Code snippet}{Code snippet of Euler's method to update the positions of the onebound model simultaneously.}
  \label{ob_struct}
\end{figure}

@@

\begin{figure}[h!]
  \begin{tabular}{c}
    \begin{lstlisting}[language=python]
      def get_near_unbinding_rate(dyn_bb) {
        dyn_ob_test = make_onebound_from_bothbound(dyn_bb) // do a fake unbind to find energy
        dG_spring = dyn_ob_test.get_PE() - dyn_bb.get_PE()
        low_affinity_unbinding_preexponential_factor = low_affinity_unbinding_rate / exp(1.0)
        return low_affinity_unbinding_preexponential_factor*exp(-dG_spring/kb/T)
      }
      def transition_bothbound_to_onebound(dyn_bb) {
        random_number = rand(0,1)
        if (random_number < get_unbinding_rate(dyn_bb)) {
          return make_onebound_from_bothbound(dyn_bb)
        }
        else return 0
      }
    \end{lstlisting}
  \end{tabular}
  \caption{Code snip}{Code snippet of transition rate calculation using the Arrhenius equation.}
  \label{transition-rate-snippet}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{c}
    \begin{lstlisting}[language=C++]
      T = cm*(nma - nma_eq);
      f1 = T/Ls;
      f2 = T/Lt;
      f1x = f1 * sin(bba);
      f1y = f1 * -cos(bba);
      f2x = f2 * sin(bma);
      f2y = f2 * -cos(bma);
      f.bbx += f1x;
      f.bby += f1y;
      f.tx  += f2x;
      f.ty  += f2y;
      f.bmx += -(f1x + f2x); // equal and opposite forces
      f.bmy += -(f1y + f2y);
    \end{lstlisting}
  \end{tabular}
  \caption{Snip}{Code snippet of internal force calculation.}
  \label{transition-rate-snippet}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
    \caption{Onebound average spring energy.}{Average domain PE of onebound model converging to $\frac12 k_BT$ energy over time.}
  \end{minipage}
  \hspace{.2cm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
    \caption{Bothbound average spring energy.}{Total domain PE of bothbound model converging to $\frac12 k_BT$ energy over time.}
  \end{minipage}
  \label{fig:equipartition_agreement}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| c | c | c | c |}
    \hline
    Author & Conditions & Velocity & Run length\\\hline
    Qiu \cite{weihongpaper} & 1mM [ATP] & $134 \pm 60.4$ nm & $1.06 \pm 0.044 \mu m$\\ \hline
    Reck-Peterson \cite{reck2006single} & 1mM [ATP] & $85 \pm 30 nm/s$  & $1.9 \pm 0.2 \mu m$\\ \hline
  \end{tabular}
  \caption{Literature values for experimental dynein stepping behavior.}{Table of literature values for dynein behavior}
  \label{table:parameter-table}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l | l | l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
    $L_s$ & 12nm & & & 21.0nm & 22.1nm & & & \\ \hline
    $L_t$ &  7nm & & & & 11.15nm & & & \\ \hline
    $R_b$ &  & & & 1.57nm & 1.45nm & & & \\ \hline
    $R_m$ &  7nm & & & 7.36nm & 6.3nm & & & \\ \hline
    $R_t$ &  & & & & 2.16nm & & & \\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & & & & & 160\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & & & & & 136\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & & & & & \\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & & & & & \\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & & & & $90.2 \pm 4.5$& \\ \hline
    $k_b$ & $460 s^{-1,b}$ & & & & & & & \\ \hline
    $c_t$ & & & & & & & & \\ \hline
    $c_m$ & & & & & & & & \\ \hline
    $c_b$ & & & & & & 140 kJ/mol & & \\ \hline
  \end{tabular}
  \caption{Literature values for dynein model parameters.}{Table of literature values for various free parameters in dynein model.}
  \label{table:parameter-table}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l |}
    \hline
    T & [ATP] \\ \hline
    310.15 K & $1mM$\\ \hline
  \end{tabular}
  \caption{Physical constants of simulation.}{Table of physical constants used in simulation.}
  \label{table:parameter-table}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../../figures/SarlahParameterTable.png}
  \caption{Sarlah kinetic rates.}{Kinetic rates used in Sarlah \textit{et. al.}'s model \cite{sarlahmodel}.}
  \label{fig:sarlah-rate-table}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| c | c | c | c | c | c |}
    \hline
    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
    134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
  \end{tabular}
  \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
  \label{table:parameter-table}
\end{figure}
